### 2016-07-18 version0.0/asli.tex
Compeleted

\newcommand{\makeacknowlege} { 1) Pauline
2) Els, Sophia, Hossein,
3)I would like to thank all my Friends in Western. Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam(s) , Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
4) bacheha
5) western ppl; Jodi, Brian, Henry, Phin,...
6) Mohad, shahin, pejman, pouria, masood,babak
7) fako famil
}
\newcommand{\makededications} {

>>>>

\newcommand{\makeacknowlege} {

This is the first or second page to be read, but the last one written. 
I will try to thank all the people that helped me to start studying Astronomy, and gave me courage to continuing this process.
My most gratitude goes to my awesome supervisor, Prof. Pauline Barmby, for all the support, during the last four years.
The amount I learned from her, her knowledge and superb physical intuition is incalculable.
She is truly one of the best supervisors in the world.

I also would like to thank you all my collaborators Prof. E. Peeters, Dr. S. Lianue, and Dr. H. Teimoorinia for not only helping me on forwarding my projects, but also thought me how a good scientist works. 
Thank you to Dr. D. Stock and Dr. M. Azimlue for all their helps and comments

I would like to thank all my fellow graduate students in Western University; Aycha, Beth, Boshra, Dimuthu, Fereshteh, Ghazal, Hoori, Javad, Laura, Maryam(s), Matt, Neven, Parshati, Pubu, Robin, Sina, Sham, Taylor and Zahra.
You guys are amazing; you helped me whenever I needed, and I had so much fun hanging out with you.
Thank you Western Physics and Astronomy department staff, especially Clara Buma, Brian Davis, Jodi Guthrie, Henry Leparskas, and Phin Perquin for helping me with problems an international student can have.

I always consider myself a lucky person because of my amazing teachers and friends.
I am particularly grateful to my astronomy teachers, Shahin, Mohadesseh, Pejman, Pouria, Masoud and Babak, the first group of people who showed me the wonders of the universe

My dearest friend, Nazanin P., my thanks goes to you and your family.
During our 18 years of friendship you always encouraged me and be there for me If I needed anything. 
Your help when I was applying for graduate school and when I moved to Canada, was priceless. You are the loveliest family in the world.
Matin, Sogol, Mercedeh, Alireza, Farhad and Ardeshir thank you for always finding a way to remind me my dreams when I was too busy or too tiered to continue.

Last but not least, I want to thank my family. 
My father, who thought me to learn from my  mistakes and do not repeat them again.
My mother, who is always available to talk to me and make me feel better. 
Setareh, who I hope that she knows that I am here in this stage of my life all because of her believe in me.
Seti, "aroosakam", my little secret keeper, whom I trust by all my heart.
Mehdi, the greatest brother (in-law) in the world.
And Radvin and Ronika for being my main source of happiness during these years.
Love you.
I would also like to thank, my grandmother, uncles, aunts and cousins for always having my back.

}
\newcommand{\makededications} {
